Incentivizing Exploration with Unbiased History

### 2018-10-09 model.tex
add info graph

\xhdr{Restrictions on the messages.} We classify recommendation policies according to what messages are allowed. 
\begin{itemize}
\item \textbf{Full history:} We show each agent the history of all previous agents' pulls. We call this policy \ALGG. 
\item \textbf{Unbiased sub-history:} We show each agent only a subset of history. The subsets are pre-determined before any arms are pulled.  
\end{itemize}

>>>>

\xhdr{Restrictions on the messages.} We classify recommendation policies according to what messages are allowed. 
\begin{itemize}
\item \textbf{Full history:} We show each agent the history of all previous agents' pulls. We call this policy \ALGG. 
\item \textbf{Unbiased sub-history:} We show each agent only a subset of history. The subsets are pre-determined before any arms are pulled.  
\item \textbf{Info graph:} All the recommendation policies in this paper can be described by an undirected transitive graph with $T$ nodes. We call it the info graph. The $T$ nodes in the graph represent the $T$ agents. If there is an edge between node $u$ and $v$ for $u < v$, it means the history of agent $u$ is shown to agent $v$.
\end{itemize}
